### 2013-07-05 Tex/chapters/results.tex
gamma ermitteln, durch powerlaw fit durch chi_max

For evaluation the Monte Carlo simulation is run until the system
is equilibrated after \(t_{eq}\) sweeps. Then the simulation continues
and the magnetisation per site \(m=\frac{1}{N}\sum_i s_i\) and energy
per site \(E=\frac{1}{N}\hat H\) are calculated and saved for every
\(2\tau\) sweeps. Where \(\tau\) denotes the \emph{autocorrelation time}
(see also \ref{ssec:eqtime}). The used values for different system sizes
are listed in tab. \ref{tab:tauAndTeq} in numbers of sweeps. Note that
the \(t_{eq}\) values are generously rounded up to be on the safe side
and the \(\tau\) values are determined as the maximum \(\tau\) over all
simulated temperatures and disorder parameters \(\tau = \underset{T,\sigma}{\max} \{\tau_{T,\sigma}\}\)
and rounded up to the next integer.
    \begin{tabular}{l r r r r r}
        \(L\)    & 16 &  32 &  64 & 128 & 256\\
        \(\tau\) &  3 &   5 &   7 &  12 &  16\\
        \(t_{eq}\) & 40 & 100 & 100 & 200 & 600\\
    \caption{Autocorrelation Times $\tau$ and Equilibration Times $t_{eq}$}
    \label{tab:tauAndTeq}
In \ref{fig:autocorr}\subref{fig:autocorr:temperatures}
the autocorrelation time for \(\sigma=0\) is plotted.
%The \emph{critical slowing down} is visible as a peak.
The plateau at low temperatures is easy to understand considering the
effects of the Wolff algorithm. At low temperatures it flips nearly every
spin in every step, thus the correlation drops to zero after one sweep.
Alternatively the parallel tempering algorithm swaps spin configurations
with possibly different signs, thus having the same effect.
Also note that the maximum of \(\tau\) is not at \(T_c\) but at a higher
temperature. The cause is probably the effectiveness of the Wolff cluster
algorithm at \(T_c\).
Obiviously the autocorrelation time \(\tau\) increases with the system
size. In fact it obeys a power law, which is the expected behaivior of
a dynamical critical exponent \(z\) as mentioned in section \ref{ssec:eqtime}.
In fig. \ref{fig:autocorr}\subref{fig:autocorr:powerLaw} \(\tau\) is plotted
over \(L\) and the dynamical exponent \(z'\) is determined as \(z'=0.64(2)\).
This exponent is much higher than the one of Wolff cluster
algorithm at criticality, which is \(z=0.25\)\cite{NewmanBarkema1999}.
So it represents the dynamical exponent for parallel tempering with
Metropolis above criticality and thus is not exactly a critical exponent.
Nevertheless it is interesting, that it obeys a power law just the same.
Anyhow it is a proof for the effectiveness of the Wolff cluster algorithm
at criticality.
    \subfigure[in dependence on the temperature $T$][]
        \label{fig:autocorr:temperatures}
        \includegraphics[width=0.45\textwidth]{plots/autocorrT}
    \subfigure[in dependence on the system size $L$][]
        \label{fig:autocorr:powerLaw}
        \includegraphics[width=0.45\textwidth]{plots/autocorrL}
    \caption[The autocorrelation time $\tau$]
        Dependece of the autocorrelation time $\tau$ on
        \subref{fig:autocorr:temperatures} the temperature $T$ for
            $\sigma=0$ and
        \subref{fig:autocorr:powerLaw} the system size $L$ (errorbars
            are the standard error determined by bootstrapping)
    \label{fig:autocorr}
For every observable \(O\) the expected value \(\avg{O}\) is determined
as the mean of \(N_{\mathrm{measure}}=10000\) measurements for \(L=16,32\)
or \(N_{\mathrm{measure}}=5000\) for \(L=64,128\). The number of
calculated sweeps totals to
\[N_{\mathrm{sweeps}}=t_{eq}+2\tau N_{\mathrm{measure}}\]
The expected values \(\avg{O}\) for \(100\) different random proximity
graphs with the same disorder paramter \(\sigma\) are then averaged to
\(\overline{\avg{O}}\).
All errorbars are estimated by bootstrapping\cite{Bootstrap} with 200
bootstrap samples if not noted otherwise.

@@

    trasition. This is stronger for smaller system sizes, as is visible
    in fig. \ref{fig:smeared_out}\subref{sfig:smeared_out:meanM}. Clearly
    the \(L=16\) curve is much less steep than the \(L=128\) curve.\\

@@

\subsection{Critical Temperature}
\label{ssec:binderIntersections}
    The evaluation of the Binder cumulant's intersections, yields the
    critical temperatures \(T_c\).
    In this section these \(T_c\) on either the Relative Neighborhood
    graph or the Gabriel graph are compared. In the following figures,
    the Relative Neighborhood graph will always be on the left side
    and the Gabriel graph on the right side.
    In fig. \ref{fig:Tc} \(T_c\) is plotted over \(\sigma\).
    \begin{figure}[htbp]
        \centering
        \subfigure[][]
        {
            \label{sfig:Tc:RNG}
            \includegraphics[width=0.45\textwidth]{plots/RNG_Tc}
        }
        \subfigure[][]
        {
            \label{sfig:Tc:GG}
            \includegraphics[width=0.45\textwidth]{plots/GG_Tc}
        }
        \caption[Critical Temperature over different disorder parameters]
        {
            Critical temperatures \(T_c\) over different
            disorder parameters \(\sigma\) for
            \subref{sfig:Tc:RNG} the Relative Neighborhood Graph and
            \subref{sfig:Tc:GG} the Gabriel Graph.\\
        }
        \label{fig:Tc}
    \end{figure}\\
    One sees that the Relative Neighborhood graph on the left has
    generally a lower critical temperature than the Gabriel. Also \(T_c\)
    of the Relative Neighborhood graph decreases
    monotonically while \(T_c\) of the Gabriel rises at first.
    For big \(\sigma\) the displaced nodes approache the limit of randomly
    distributed nodes, hence \(T_c\) is independent of \(\sigma\) for
    \(\sigma >> 1\).\\
    A strange property is the jump from \(\sigma = 0\) to \(\sigma > 0\)
    of \(T_c\) on the Gabriel graph. To understand that, one has to
    consider the influence of the graph properties on the critical
    temperature.\\
    A characteristic property of a graph is it's degree \(K\).
    The degree \(K\) of a graph -- sometimes called \emph{coordination number} --
    is defined as the mean count of neighbors per node
    \begin{equation}
        K = \frac{\sum_{\avg{i,j}} 1}{\sum_{i} 1}
        \label{eq:degree}
    \end{equation}
    Therefore the degree of the graphs at different \(\sigma\) is
    plotted in fig. \ref{fig:Tc_deg}\subref{sfig:deg:RNG}\subref{sfig:deg:GG}.
    \begin{figure}[htbp]
        \centering
        \subfigure[][]
        {
            \label{sfig:deg:RNG}
            \includegraphics[width=0.45\textwidth]{plots/RNG_deg}
        }
        \subfigure[][]
        {
            \label{sfig:deg:GG}
            \includegraphics[width=0.45\textwidth]{plots/GG_deg}
        }

@@

        \caption[Critical Temperature over different disorder parameters]
        {
            Top: Degree \(K\) of graph over different
            disorder parameters \(\sigma\) for
            \subref{sfig:deg:RNG} the Relative Neighborhood Graph and
            \subref{sfig:deg:GG} the Gabriel Graph.\\
            Bottom: Critical temperatures normalized by degree over different
            disorder parameters for
            \subref{sfig:Tc_norm_deg:RNG} the Relative Neighborhood Graph and
            \subref{sfig:Tc_norm_deg:GG} the Gabriel Graph.
        }
        \label{fig:Tc_deg}
    \end{figure}\\
    \(T_c\) and \(K\) are evidently correlated. This is not
    unexpected. For example the Honeycomb lattice, for which exsists an
    anlytical solution \cite{Wannier1945} and has a degree of 3, has a
    critical temperature of
    \begin{equation}
        \cosh\brac{\frac{J}{T_c}}=2 \overset{J=1}{\Longrightarrow} T_c \approx 1.52
        \label{eq:exactHCTc}
    \end{equation}
    This is lower than for the square lattice with degree 4.\\
    It seems resonable to normalize \(T_c\) by the degree of the underlying
    graph. This is done in fig \ref{fig:Tc_deg}\subref{sfig:Tc_norm_deg:RNG}\subref{sfig:Tc_norm_deg:GG}.
    Indeed the normalisation eliminates the jump and reduces the
    slope of the rising on the Gabriel graph. Hence it reduces differences
    between the Relative Neighborhood graph and the Gabriel graph.\\
    % Zitat, dass Janke das auch gemacht hat .. nochmal nachlesen
    The jump of \(K\) and therefore the jump of \(T_c\) on the Gabriel graph is easily explained
    by the definition of the Gabriel graph and it's aftereffects for
    the transition from \(\sigma = 0\). Visible in fig. \ref{fig:GG_sigma}
    a small change of sigma causes many new egdes to arise\footnote{See also \url{http://www.youtube.com/watch?v=PcVZ2pG11GI} for an animation.}.
    To fully understand this, take four nodes forming a square. The edge
    across does not exist, because the other two nodes are on the edge
    of the lune. Moving one node slightly into the square, causes the lune
    to get smaller, hence no other nodes are inside or on the edge of
    the lune anymore and the edge appears.
    \begin{figure}[htbp]
        \centering
        \subfigure[][]
        {
            \label{sfig:GG_sigma:zero}
            \includegraphics[width=0.40\textwidth]{images/GG/sigma_e0}
        }
        \subfigure[][]
        {
            \label{sfig:GG_sigma:notzero}
            \includegraphics[width=0.40\textwidth]{images/GG/sigma_g0}
        }
        \caption[Anomaly of the Gabriel graph for small $\sigma$]
        {
            Gabriel graph with periodic boundary conditions for
                \subref{sfig:GG_sigma:zero} \(\sigma = 0\)
                \subref{sfig:GG_sigma:notzero} \(\sigma = 0.01\)
        }
        \label{fig:GG_sigma}
    \end{figure}\\
    But the degree does not alone influence the behavior of \(T_c\).
    Further \(T_c\) depends on the coupling
    constant \(J\), which is obvious in eq. \eqref{eq:exactTc} and
    \eqref{eq:exactHCTc}. Therefore  in fig. \ref{fig:TcJ}\subref{sfig:sumJ:RNG}\subref{sfig:sumJ:GG}
    the mean sum of the coupling constants to all neighbors \(\avg{\sum_{\avg{i,j}} J_{ij}}\)
    is plotted. This is a number which should combine the dependence on
    the degree and the coupling constant, which is not equal for
    every edge in this case.
    The plots fig \ref{fig:TcJ}\subref{sfig:Tc_normJ:RNG}\subref{sfig:Tc_normJ:GG}
    show that \(\avg{\sum_{\avg{i,j}} J_{ij}}\) is also correlated with \(T_c\).
    \begin{figure}[htbp]
        \centering
        \subfigure[][]
        {
            \label{sfig:sumJ:RNG}
            \includegraphics[width=0.45\textwidth]{plots/RNG_sumJ}
        }
        \subfigure[][]
        {
            \label{sfig:sumJ:GG}
            \includegraphics[width=0.45\textwidth]{plots/GG_sumJ}
        }

@@

        \caption[Critical Temperature over different disorder parameters]
        {
            Top: Mean sum of the coupling constants to all
            neighbors over different disorder parameters for
            \subref{sfig:sumJ:RNG} the Relative Neighborhood Graph and
            \subref{sfig:sumJ:GG} the Gabriel Graph.\\
            Bottom: Critical temperatures normalized by mean sum of the
            coupling constants \(\avg{\sum_{\avg{i,j}} J_{ij}}\) over different
            disorder parameters for
            \subref{sfig:Tc_normJ:RNG} the Relative Neighborhood Graph and
            \subref{sfig:Tc_normJ:GG} the Gabriel Graph.
        }
        \label{fig:TcJ}
    \end{figure}\\
    % I don't know what all that means...
    If on normalizes \(T_c\) with \(\avg{\sum_{\avg{i,j}} J_{ij}}\) as in
    \ref{fig:TcJ}\subref{sfig:Tc_normJ:RNG}\subref{sfig:Tc_normJ:GG}, the
    jump on the Gabriel graph arises again, but \(T_c\) is now monotonically
    decreasing with increasing disorder parameter \(\sigma\). Moreover
    the forms of both curves are quite similar, but the
    one for the Relative Neighborhood graph \ref{fig:TcJ}\subref{sfig:Tc_norm:RNG}
    is generally lower and spans over a bigger temperature range than
    the curve of the Gabriel graph \ref{fig:TcJ}\subref{sfig:Tc_norm:GG}.
    % Warum??? Die eigenschaften des Graphen sollten mit der Normalisierung erledigt sein.
    % RNG: laengere Kanten -> weniger lokale effekte?
    Both graph types have a plateau at \(0 < \sigma < 0.1\). So small
    disorder has little influence on this normalized critical temperature.
    Also both graph types have a steep decline after the plateau before
    they approache an asymptotic limit for \(\sigma >> 1\)\\\\

    %~ But once the degree of
    %~ the graph and hence the mean sum of the coupling constants decreases,
    %~ the normalized critical temperature decreases, too.\\
    %~ In conclusion the critical temperature depends on the averaged sum
    %~ of the coupling constant \(\avg{\sum_{\avg{i,j}} J_{ij}}\). But after
    %~ normalizing it with this, the plots for both proximity graphs look
    %~ similar.
    % The author is not sure what it means.

\subsection{Critical Exponents}
    For \(\sigma \in \{0,0.1,0.2,0.3,0.5,1.0\}\) a finite size scaling analysis was
    performed to determine the critical exponents \(\beta, \gamma, \nu\)
    using \texttt{autoscale.py} \cite{autoscale2009}. The values for
    \(\sigma = 0\) are analytically known \cite{Pelissetto2002}. The
    values for all other \(\sigma\) should be the same as for \(\sigma = 0\)
    like mentioned before in section \ref{ssec:finitesize}.
    The values for \(\sigma\) are chosen to represent every interesting
    region from fig. \ref{fig:Tc}\subref{sfig:Tc_norm:RNG}\subref{sfig:Tc_norm:GG}:
    the plateau at small \(\sigma\), the steep decline and the plateau at
    big \(\sigma\).\\
    Like in tab. \ref{tab:critExp} to see, most values
    are matching the expectations. Most \(\beta\) seem to be a bit too
    big, but they are close enough to the expectations to be explained
    by the fact that small systems (\(L=32,64\)) were used for the
    analysis.
    Anyway, two critical exponents are sufficient to determine the universality
    class. Therefore this disordered Ising modell is in the same universality
    class as the standard Ising ferromagnet \cite[p. 145]{Katzgraber2011}.
    \begin{table}[htbp]
        \center
        \begin{tabular}{l l l l l}
            \toprule
             & \multicolumn{1}{c}{\(\sigma\)} & \multicolumn{1}{c}{\(\nu\)} & \multicolumn{1}{c}{\(\gamma\)} & \multicolumn{1}{c}{\(\beta\)}\\
            \midrule
            exact (\cite[p. 59]{Pelissetto2002}) & \multicolumn{1}{c}{\(0\)} & \multicolumn{1}{c}{\(1\)} & \multicolumn{1}{c}{\(-\frac{7}{4}\)} & \multicolumn{1}{c}{\(\frac{1}{8}\)}\\
            \midrule
            Gabriel      & 0.0 & 1.008(4) & -1.735(2) & 0.1262(4)\\
                         & 0.1 & 1.02(1)  & -1.744(5) & 0.133(6) \\
                         & 0.3 & 1.000(5) & -1.724(16)& 0.129(12)\\
                         & 0.5 & 1.009(8) & -1.750(12)& 0.125(13)\\
                         & 1.0 & 1.015(22)& -1.743(17)& 0.123(16)\\
            \midrule
            Relative N.  & 0.0 & 1.007(2) & -1.740(2) & 0.130(1) \\
                         & 0.1 & 0.99(1)  & -1.746(5) & 0.133(4) \\
                         & 0.2 & 1.022(17)& -1.756(14)& 0.123(10)\\
                         & 0.5 & 1.002(17)& -1.750(16)& 0.143(13)\\
                         & 1.0 & 1.011(20)& -1.758(16)& 0.138(13)\\
            \bottomrule
        \end{tabular}
        \caption{Critical exponents for different $\sigma$}
        \label{tab:critExp}
    \end{table}

>>>>

For evaluation the Monte Carlo simulation is run until the system
is equilibrated after \(t_{eq}\) sweeps. Then the simulation continues
and the magnetization per site \(m=\frac{1}{N}\sum_i s_i\) and energy
per site \(E=\frac{1}{N}\hat H\) are calculated and saved for every
\(2\tau\) sweeps. Where \(\tau\) denotes the \emph{autocorrelation time}
(see also \ref{ssec:eqtime}). The used values for different system sizes
are listed in tab. \ref{tab:tauAndTeq} in numbers of sweeps. Note that
the \(t_{eq}\) values are generously rounded up to be on the safe side
and the \(\tau\) values are determined as the maximum \(\tau\) over all
simulated temperatures and disorder parameters \(\tau = \underset{T,\sigma}{\max} \{\tau_{T,\sigma}\}\)
and rounded up to the next integer.
\begin{table}[htbp]
    \center
    \begin{tabular}{l r r r r r}
        \toprule
        \(L\)    & 16 &  32 &  64 & 128 & 256\\
        \midrule
        \(\tau\) &  3 &   5 &   7 &  12 &  16\\
        \(t_{eq}\) & 40 & 100 & 100 & 200 & 600\\
        \bottomrule
    \end{tabular}
    \caption{Autocorrelation Times $\tau$ and Equilibration Times $t_{eq}$}
    \label{tab:tauAndTeq}
\end{table}\\
For every observable \(O\) the expected value \(\avg{O}\) is determined
as the mean of \(N_{\mathrm{measure}}=10000\) measurements for \(L=16,32\)
or \(N_{\mathrm{measure}}=5000\) for \(L=64,128\). The number of
calculated sweeps totals to
\[N_{\mathrm{sweeps}}=t_{eq}+2\tau N_{\mathrm{measure}}\]
The expected values \(\avg{O}\) for \(100\) different random proximity
graphs with the same disorder parameter \(\sigma\) are then averaged to
\(\overline{\avg{O}}\). Not only the seed to generate the new random
realization of the proximity graph gets changed, but also the seed for
the random numbers used in the Monte Carlo simulation and during the
generation of the random start configuration of the spins.\\
The errors \(\Delta \overline{\avg{O}}\) are estimated by bootstrapping
\cite{Bootstrap} with 200 bootstrap samples if not noted otherwise.
Note that while \(\Delta \avg{O}\) is dependend on \(\tau\) \cite[p. 151]{Katzgraber2011}
\(\Delta \overline{\avg{O}}\) is not directly, because it is averaged
over different realizations of the random proximity graph, which are
surely uncorrelated.
Because every error mentioned in this thesis is of this type, it is not
necessary to determine \(\tau\) for each observable. Therefore a good
error estimate can be achieved by simple bootstrapping. Though one has
to simulate enough uncorrelated states for each realization, to keep
the \(\Delta \overline{\avg{O}}\) small.

\subsection{Short Analysis of the Autocorrelation Time  $\tau$}
    % Sollte das hier rein?
    Before the results are presented, a short analysis of the
    autocorrelation time \(\tau\) is given, to illustrate the benefits
    of the used Wolff cluster algorithm.\\
    In \ref{fig:autocorr}\subref{fig:autocorr:temperatures}
    the autocorrelation time for the magnetization per site \(m\) at \(\sigma=0\) is plotted.
    \begin{figure}[htbp]
        \centering
        \subfigure[in dependence on the temperature $T$][]
        {
            \label{fig:autocorr:temperatures}
            \includegraphics[width=0.45\textwidth]{plots/autocorrT}
        }
        \subfigure[in dependence on the system size $L$][]
        {
            \label{fig:autocorr:powerLaw}
            \includegraphics[width=0.45\textwidth]{plots/autocorrL}
        }
        \caption[The autocorrelation time $\tau$]
        {
            Dependece of the autocorrelation time $\tau$ on
            \subref{fig:autocorr:temperatures} the temperature $T$ for
                $\sigma=0$ and
            \subref{fig:autocorr:powerLaw} the system size $L$ (errorbars
                are the standard error determined by bootstrapping)
        }
        \label{fig:autocorr}
    \end{figure}
    The plateau at low temperatures is easy to understand considering the
    effects of the Wolff algorithm. At low temperatures it flips nearly every
    spin in every step, thus the correlation drops to zero after one sweep.
    Alternatively the parallel tempering algorithm swaps spin configurations
    with possibly different signs, thus having the same effect.
    Also note that the maximum of \(\tau\) is not at \(T_c\) but at a higher
    temperature. The cause is probably the effectiveness of the Wolff cluster
    algorithm at \(T_c\).
    Obviously the autocorrelation time \(\tau\) increases with the system
    size. In fact it obeys a power law, which is the expected behaivior of
    a dynamical critical exponent \(z\) as mentioned in section \ref{ssec:eqtime}.
    In fig. \ref{fig:autocorr}\subref{fig:autocorr:powerLaw} \(\tau\) is plotted
    over \(L\) and the dynamical exponent \(z'\) is determined as \(z'=0.64(2)\).
    This exponent is much higher than the one of Wolff cluster
    algorithm at criticality, which is \(z=0.25\)\cite{NewmanBarkema1999}.
    So it represents the dynamical exponent for parallel tempering with
    Metropolis above criticality and thus is not exactly a critical exponent.
    Nevertheless it is interesting, that it obeys a power law just the same.
    Anyhow it is a proof for the effectiveness of the Wolff cluster algorithm
    at criticality.

@@

    transition. This is stronger for smaller system sizes, as is visible
    in fig. \ref{fig:smeared_out}\subref{sfig:smeared_out:meanM}\footnote{See the appendix \ref{appendix:finiteSizeEffects} for a similar figure for the specific heat.}.
    Clearly the \(L=16\) curve is much less steep than the \(L=128\) curve.\\

@@

\subsection{Critical Temperature}
\label{ssec:binderIntersections}
    The evaluation of the Binder cumulant's intersections, yields the
    critical temperatures \(T_c\).
    In this section these \(T_c\) on either the Relative Neighborhood
    graph or the Gabriel graph are compared. In the following figures,
    the Relative Neighborhood graph will always be on the left side
    and the Gabriel graph on the right side.
    In fig. \ref{fig:Tc} \(T_c\) is plotted over \(\sigma\).
    \begin{figure}[htbp]
        \centering
        \subfigure[][]
        {
            \label{sfig:Tc:RNG}
            \includegraphics[width=0.45\textwidth]{plots/RNG_Tc}
        }
        \subfigure[][]
        {
            \label{sfig:Tc:GG}
            \includegraphics[width=0.45\textwidth]{plots/GG_Tc}
        }
        \caption[Critical Temperature over different disorder parameters]
        {
            Critical temperatures \(T_c\) over different
            disorder parameters \(\sigma\) for
            \subref{sfig:Tc:RNG} the Relative Neighborhood Graph and
            \subref{sfig:Tc:GG} the Gabriel Graph.\\
        }
        \label{fig:Tc}
    \end{figure}\\
    One sees that the Relative Neighborhood graph on the left has
    generally a lower critical temperature than the Gabriel. Also \(T_c\)
    of the Relative Neighborhood graph decreases
    monotonically while \(T_c\) of the Gabriel rises at first.
    For big \(\sigma\) the displaced nodes approach the limit of randomly
    distributed nodes, hence \(T_c\) is independent of \(\sigma\) for
    \(\sigma >> 1\).\\
    A strange property is the jump from \(\sigma = 0\) to \(\sigma > 0\)
    of \(T_c\) on the Gabriel graph. To understand that, one has to
    consider the influence of the graph properties on the critical
    temperature.\\
    One basic property of a graph is it's degree \(K\) -- sometimes
    called \emph{coordination number} -- is defined as the mean count of
    neighbors per node
    \begin{equation}
        K = \frac{\sum_{\avg{i,j}} 1}{\sum_{i} 1}
        \label{eq:degree}
    \end{equation}
    It is known, that the degree has an impact on the critical Temperature.
    For example the Honeycomb lattice is of degree \(K=3\)
    and there exists an analytic solution \cite{Wannier1945}.
    It's a critical temperature is determined by eq. \eqref{eq:exactHCTc}.
    \begin{equation}
        \cosh\brac{\frac{J}{T_c}}=2 \overset{J=1}{\Longrightarrow} T_c \approx 1.52
        \label{eq:exactHCTc}
    \end{equation}
    This is lower than for the square lattice with degree 4.\\
    If one plots the degree of the graphs at different \(\sigma\) like
    in fig. \ref{fig:Tc_deg}\subref{sfig:deg:RNG}\subref{sfig:deg:GG},
    one recognizes, that \(T_c\) and \(K\) are evidently correlated.
    It seems reasonable to normalize \(T_c\) by the degree of the underlying
    graph. This is done in fig \ref{fig:Tc_deg}\subref{sfig:Tc_norm_deg:RNG}\subref{sfig:Tc_norm_deg:GG}.
    Indeed the normalization eliminates the jump and reduces the
    slope of the rising on the Gabriel graph. Hence it reduces differences
    between the Relative Neighborhood graph and the Gabriel graph.
    \begin{figure}[htbp]
        \centering
        \subfigure[][]
        {
            \label{sfig:deg:RNG}
            \includegraphics[width=0.45\textwidth]{plots/RNG_deg}
        }
        \subfigure[][]
        {
            \label{sfig:deg:GG}
            \includegraphics[width=0.45\textwidth]{plots/GG_deg}
        }

@@

        \caption[Critical Temperature normalized by Degree of the Graph]
        {
            Top: Degree \(K\) of graph over different
            disorder parameters \(\sigma\) for
            \subref{sfig:deg:RNG} the Relative Neighborhood Graph and
            \subref{sfig:deg:GG} the Gabriel Graph.\\
            Bottom: Critical temperatures normalized by degree over different
            disorder parameters for
            \subref{sfig:Tc_norm_deg:RNG} the Relative Neighborhood Graph and
            \subref{sfig:Tc_norm_deg:GG} the Gabriel Graph.
        }
        \label{fig:Tc_deg}
    \end{figure}\\
    To understand the jump of \(T_c\), it seems to be sufficient to
    understand the jump of \(K\), which is easily explained
    by the definition of the Gabriel graph and it's aftereffects for
    the transition from \(\sigma = 0\). Visible in fig. \ref{fig:GG_sigma}
    a small change of \(\sigma\) causes many new edges to arise\footnote{See also \url{http://www.youtube.com/watch?v=PcVZ2pG11GI} for an animation.}.
    To fully understand this, take four nodes forming a square. The edge
    across does not exist, because the other two nodes are on the edge
    of the lune. Moving one node slightly into the square, causes the lune
    to get smaller, hence no other nodes are inside or on the edge of
    the lune anymore and the edge appears.
    \begin{figure}[htbp]
        \centering
        \subfigure[][]
        {
            \label{sfig:GG_sigma:zero}
            \includegraphics[width=0.40\textwidth]{images/GG/sigma_e0}
        }
        \subfigure[][]
        {
            \label{sfig:GG_sigma:notzero}
            \includegraphics[width=0.40\textwidth]{images/GG/sigma_g0}
        }
        \caption[Anomaly of the Gabriel graph for small $\sigma$]
        {
            Gabriel graph with periodic boundary conditions for
                \subref{sfig:GG_sigma:zero} \(\sigma = 0\)
                \subref{sfig:GG_sigma:notzero} \(\sigma = 0.01\)
        }
        \label{fig:GG_sigma}
    \end{figure}\\
    But the degree does not alone influence the behavior of \(T_c\).
    Further \(T_c\) depends on the coupling constant \(J\), which is
    obvious in eq. \eqref{eq:exactTc} and \eqref{eq:exactHCTc}. The
    coupling constant in turn is depending on the length of the edges,
    which changes with \(\sigma\).
    Therefore  in fig. \ref{fig:TcJ}\subref{sfig:sumJ:RNG}\subref{sfig:sumJ:GG}
    the mean sum of the coupling constants to all neighbors \(\avg{\sum_{\avg{i,j}} J_{ij}}\)
    is plotted. This is a number which should combine the dependence on
    the degree and the coupling constant.
    The plots fig \ref{fig:TcJ}\subref{sfig:Tc_normJ:RNG}\subref{sfig:Tc_normJ:GG}
    show that \(\avg{\sum_{\avg{i,j}} J_{ij}}\) is also correlated with \(T_c\).
    \begin{figure}[htbp]
        \centering
        \subfigure[][]
        {
            \label{sfig:sumJ:RNG}
            \includegraphics[width=0.45\textwidth]{plots/RNG_sumJ}
        }
        \subfigure[][]
        {
            \label{sfig:sumJ:GG}
            \includegraphics[width=0.45\textwidth]{plots/GG_sumJ}
        }

@@

        \caption[Critical Temperature normalized by Mean Sum of the Coupling Constants]
        {
            Top: Mean sum of the coupling constants to all
            neighbors over different disorder parameters for
            \subref{sfig:sumJ:RNG} the Relative Neighborhood Graph and
            \subref{sfig:sumJ:GG} the Gabriel Graph.\\
            Bottom: Critical temperatures normalized by mean sum of the
            coupling constants \(\avg{\sum_{\avg{i,j}} J_{ij}}\) over different
            disorder parameters for
            \subref{sfig:Tc_normJ:RNG} the Relative Neighborhood Graph and
            \subref{sfig:Tc_normJ:GG} the Gabriel Graph.
        }
        \label{fig:TcJ}
    \end{figure}\\
    If one normalizes \(T_c\) with \(\avg{\sum_{\avg{i,j}} J_{ij}}\) as in
    \ref{fig:TcJ}\subref{sfig:Tc_normJ:RNG}\subref{sfig:Tc_normJ:GG}, the
    jump on the Gabriel graph arises again, but \(T_c\) is now monotonically
    decreasing with increasing disorder parameter \(\sigma\). Moreover
    the forms of both curves are quite similar, but the
    one for the Relative Neighborhood graph \ref{fig:TcJ}\subref{sfig:Tc_norm:RNG}
    is generally lower and spans over a bigger temperature range than
    the curve of the Gabriel graph \ref{fig:TcJ}\subref{sfig:Tc_norm:GG}.
    Both graph types have a plateau at \(0 < \sigma < 0.1\). So small
    disorder has little influence on this normalized critical temperature.
    Also both graph types have a steep decline after the plateau before
    they approach an asymptotic limit for \(\sigma >> 1\)\\\\

\subsection{Critical Exponents}
    A finite size scaling analysis was
    performed to determine the critical exponents \(\beta, \gamma, \nu\)
    using \texttt{autoscale.py} \cite{autoscale2009}. The values for
    \(\sigma = 0\) are analytically known \cite{Pelissetto2002}. The
    values for all other \(\sigma\) are expected be the same as for
    \(\sigma = 0\) like mentioned before in section \ref{ssec:finitesize}.
    Therefore it is sufficient to take a few samples to test if the
    expectations are met. Hence 5 values of \(\sigma\) are analyzed,
    which are chosen to represent every interesting region from fig. \ref{fig:Tc}\subref{sfig:Tc:RNG}\subref{sfig:Tc:GG}:
    the analytically known value for \(\sigma = 0\), the in \cite{Janke1994}
    examined limit for \(\sigma \gtrsim 1\), the plateau at small
    \(\sigma\), the steep decline and the shallow decline at \(\sigma = 0.5\).\\
        \begin{tabular}{l l l l l}
             & \multicolumn{1}{c}{\(\sigma\)} & \multicolumn{1}{c}{\(\nu\)} & \multicolumn{1}{c}{\(\gamma\)} & \multicolumn{1}{c}{\(\beta\)}\\
            exact (\cite[p. 59]{Pelissetto2002}) & \multicolumn{1}{c}{\(0\)} & \multicolumn{1}{c}{\(1\)} & \multicolumn{1}{c}{\(-\frac{7}{4}\)} & \multicolumn{1}{c}{\(\frac{1}{8}\)}\\
            Gabriel      & 0.0 & 1.008(4) & -1.735(2) & 0.1262(4)\\
                         & 0.1 & 1.02(1)  & -1.744(5) & 0.133(6) \\
                         & 0.3 & 1.000(5) & -1.724(16)& 0.129(12)\\
                         & 0.5 & 1.009(8) & -1.750(12)& 0.125(13)\\
                         & 1.0 & 1.015(22)& -1.743(17)& 0.123(16)\\
            Relative N.  & 0.0 & 1.007(2) & -1.740(2) & 0.130(1) \\
                         & 0.1 & 0.99(1)  & -1.746(5) & 0.133(4) \\
                         & 0.2 & 1.022(17)& -1.756(14)& 0.123(10)\\
                         & 0.5 & 1.002(17)& -1.750(16)& 0.143(13)\\
                         & 1.0 & 1.011(20)& -1.758(16)& 0.138(13)\\
        \caption{Critical exponents for different $\sigma$}
        \label{tab:critExp}
    Like in tab. \ref{tab:critExp} to see, most values
    are matching the expectations. Especially \(\nu\) and \(gamma\)
    are always in very good agreement with their exact values. Because
    there can never be to much cross and consistency checks, the ratio
    \(\frac{\gamma}{\nu}\) is also determined, by fitting the maxima of
    the susceptibility \(\chi_{\mathrm{max}}\) by the power law \(aL^\frac{\gamma}{\nu}\).
    The results are displayed in fig. \ref{fig:susCrossCheck}. The by this
    method determined ratios confirm the by collapse obtained values.
        \subfigure[][]
            \label{sfig:susCrossCheck:RNG}
            \includegraphics[width=0.45\textwidth]{plots/RNGgammaBySus}
        \subfigure[][]
            \label{sfig:susCrossCheck:GG}
            \includegraphics[width=0.45\textwidth]{plots/GGgammaBySus}
        \caption[Alternative Way Determining $\gamma$]
            Cross checking the critical exponent $\gamma$ for
                \subref{sfig:susCrossCheck:RNG} the Relative Neighborhood graph and
                \subref{sfig:susCrossCheck:GG} the Gabriel graph.
            Dotted lines are power law fits.
        \label{fig:susCrossCheck}
    Despite the very good results for \(\nu\) and \(\gamma\), most of the
    \(\beta\) seem to be a bit too big, but they are close enough to the
    expectations to be consistent.
    Maybe their deviations can be explained by the fact that small
    systems (\(L=32,64\)) were used for the analysis, which introduce
    some deviations, because the collapse works best for big system sizes.
    Anyway, two critical exponents are sufficient to determine the
    universality class \cite[p. 145]{Katzgraber2011}. Therefore this
    disordered Ising model is in the same universality class as the
    standard Ising ferromagnet.
